---
title: "IPEG2_analysis"
author: "Bruce Peng"
date: "30/03/2020"
output: html_document
---

Here includes codes for analysis of IPEG2.

**Participants and trial numbers:**
A total of 30 participants are included in this dataset, each participants completed 40 trials thus the total number of trials is 40x30 = 1200. 34 trials were deleted due to participants' written responses did not conform to the task criteria. Thus, the total number of trials included in the analysis is 1152. 

**Data description:**
*participant:* N=30
*Sex:*: Participants' sex, Male or Female
*HS_ID*: Helping story presented during willingness to help rating on each trial
*Sim_SID:* Story presented to participants on each trial, a total of 40 stories were presented. These stories can be found in IPEG2_stimuli.xlsx
*STFace_ID*: Simulation target ID 
*ST_sex*: Sex of Simulation target (F=Female, M=Male). 
*ST_age*: Age group of Simulation target.
*HTFace_ID*: Helping target ID
*HT_sexr*: Helping target sex (Male or female)
*HT_age*: Helping target age (Old or young)
*story_conditions*: Helping story conditions  (0=not similar, 1= similar)
*Match*: Match of simulation and helping targets as well as helping and simulation story (1=Target and story mismatch, 2= Target match and story mismatch, 3= Target mismatch and story match, 4= Target and story mismatch)
*Trial:* Trial order presented to participants.
*Condition:* Imagine helping (Experimental:Imagine) and identify journalistic technique (Control:Identify)
*Detail:* "The imagined media website/scene in your mind was?" (collected for estimate and imagine helping conditions). Responses were made on a 1(simple)-7(detailed) Likert scale. 
*Coherence:* "The imagined media website/scene in your mind was?" (collected for estimate and imagine helping conditions). Responses were made on a 1(vague)-7(coherent and clear) Likert scale. 
*Perspective:*  "When you identified the media website, imagined helping, or visualized the media website and comments  did you consider  the thoughts and feelings of the person?" (collected for all conditions). Responses are made on a 1(not at all)- 7 (strongly considered). 
*Help:* DV of interest. "How likely would you be to help in this situation?" (collected for all conditions). Responses are made on a 1(not at all)- 7 (very willing) Likert scale.

Note: Detail, Coherence and Perspective are included so the proctocol mirrored previous studies as closely as possible and are not of particular interest in the current study. 

*Emotional reaction:*
Emotional reaction (collected for all conditions) rated on a 1(not at all)-7(very strongly) Likert scale for the following emotions:
-	Soft-hearted
-	Troubled 
-	Warm 
-	Distressed
-	Sympathetic
-	Compassionate
-	Disturbed
-	Tender
-	Moved
-	Worried
These measures are included to reduce the possibility of participants correctly guaging the experimental goal and are not utilized in the analyses


# Package and directory set up
```{r setup, include=FALSE}
# Load packages
if (!require(pacman)) install.packages('pacman')
pacman::p_load(tidyverse,brms, bayestestR) 

# source custom codes
source("C:/Users/dpen466/Google Drive/Phd (1)/Experiment/Studies/Data/IPE/source/Bayes_scripts.R")
```

##Data setup

```{r}
# Loading data
IPEG2.df<- read.csv('IPEG2_fulldata_N=30.csv', header=T)

# Remove deleted trials from data frame
IPEG2.df<- IPEG2.df[complete.cases(IPEG2.df$Condition),]

# Convert Story_ID and Condition vectors into factors and ensure Identify condition is set as the reference group
IPEG2.df$Sim_SID<- as.factor(IPEG2.df$Sim_SID)
IPEG2.df$HS_ID<- as.factor(IPEG2.df$HS_ID)
IPEG2.df$Conditions<- as.factor(IPEG2.df$Conditions)
levels (IPEG2.df$Conditions) <- c('Identify', 'Imagine')

# Data transformations 
## Generate the five factor variable for Match conditions
IPEG2.df$Match_condition<- IPEG2.df$Match +1
IPEG2.df$Match_condition[IPEG2.df$Conditions=="Identify"] <- 1
IPEG2.df$Match_condition <- as.factor(IPEG2.df$Match_condition)
levels(IPEG2.df$Match_condition) <- c("Identify","HT-HS-", "HT+HS-","HT-HS+", "HT+HS+")

## Effect code and dummy
IPEG2.df<- IPEG2.df%>% 
              mutate(
                # Effect code sex of helping targets(Female=1, male=-1)
                HT_sex_c= ifelse(HT_sex=='F', 1, -1),
                # Effect code age of helping targets (1=Old, -1=Young)
                HT_age_c = ifelse(HT_age=='Old', 1, -1),
                # Create a dummy variable= for the condition variable
                dummy_img = as.numeric (Conditions=='Imagine'),
                # Ordered restricted contrast
                ORM_code = ifelse(Match_condition=='Identify', "Identify",
                                  ifelse(Match_condition=='HT+HS+','HT+HS+', "Imagine")))
IPEG2.df$ORM_code <- as.factor (IPEG2.df$ORM_code)
IPEG2.df$ORM_code <- relevel(IPEG2.df$ORM_code, ref = "Identify")
```


# Generalizability of Prosoical simulation effect
```{r}
Bayes<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~Conditions+HT_sex_c+HT_age_c+(Conditions|participant)+
                      (Conditions|Sim_SID)+(Conditions|HTFace_ID)+(Conditions|STFace_ID)+(Conditions|HS_ID)) +
                   lf(disc~ 0+Conditions, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T, control=list(adapt_delta=0.99))


# Diagnostic Checks: pp check and traceplots
pp_check(Bayes);plot(Bayes)
# Rhat and sample sizes
bayes_samples(Bayes)

# Prior Predictive simulations
set.seed(67);prior_sim(Bayes, c("sd_participant", 'cor_participant', "b"))

# Results
summary(Bayes, probs=0.89)
# pd
p_direction(Bayes, parameters = "b_Conditions")
# % in ROPE
rope(Bayes,ci=1, range = c(-0.10, 0.10), parameters = "b_Conditions")

# Extract posterior samples 
set.seed(67);posterior<- posterior_samples(Bayes) 
latent_SD(posterior)


test<- hypothesis(Bayes, hypothesis = "ConditionsImagine = 0", alpha=0.055)
test;plot(test)
```
### Plots
```{r}
# Violin plots
plot.df<- as.data.frame(posterior$b_ConditionsImagine)
colnames(plot.df)<- "Posterior"
ggplot(plot.df, aes(x=1, y=Posterior)) +
                      geom_violin(trim=FALSE) +
                      geom_boxplot(width=0.1, fill="white") +
                      theme_classic() +
                      geom_hline(yintercept=0, linetype="dashed", color = "red", size=0.5) +
                      labs(x="Contrasts", y = expression(beta)) +
                      stat_boxplot(geom = "errorbar", width = 0.1, coef=0.7) + 
                      theme(legend.position = "none") +
                      xlab("Imagine Helping>Identify Media Source") +
                      scale_x_discrete(labels=c(""))
# Plot the predicted probability of each category on the outcome measure for each condition
PSE_plot<-conditional_effects(Bayes,categorical=T)
plot(PSE_plot)[[1]] +
  scale_x_discrete(labels=c("Identify Media Source", "Imagine Helping")) +
  theme_classic() +
  xlab("Simulation Conditions") +
  ylim (0, 0.45)
```

### Contrast PSE across IPE, IPEF and IPEG
```{r}
IPE_imagine.df<-readRDS(file="IPE_Imagine.rds")
IPEF_imagine.df<-readRDS(file="IPEF_Imagine.rds")
IPEG_imagine.df<- readRDS(file="IPEG_Imagine.rds")
# Violin Plot of each experiment
PSE<-cbind.data.frame('IPE'=IPE_imagine.df,
                       'IPEF'=IPEF_imagine.df,
                       'IPEG'=IPEG_imagine.df,
                       'IPEG2'= posterior$b_ConditionsImagine)
PSE.df<-PSE
PSE<- PSE %>% gather("IPE","IPEF", 'IPEG','IPEG2', key= Condition, value= Posterior)
violin_PSE<- violin_bayes(PSE)[[1]]
violin_PSE +
  labs(title="Prosocial simulation effect across experiments",x="Experiment", y = "Beta coefficient") +
  stat_boxplot(geom = "errorbar", width = 0.1, coef=0.7)

# Summaries
violin_bayes(PSE, CI_range = c(0.055, 0.945))[[2]]
# pd
p_direction(PSE.df)
# % in ROPE
rope(PSE.df,ci=1, range = c(-0.1, 0.1))
#-------------------------------------------------------------------------------------------------------------------------
# Contrasts between conditions across experiments
IPE_IPEG2<-PSE$Posterior[PSE$Condition=="IPE"]-PSE$Posterior[PSE$Condition=="IPEG2"]
IPEF_IPEG2<-PSE$Posterior[PSE$Condition=="IPEF"]-PSE$Posterior[PSE$Condition=="IPEG2"]
IPE_IPEG<-PSE$Posterior[PSE$Condition=="IPE"]-PSE$Posterior[PSE$Condition=="IPEG"]
IPEF_IPEG<-PSE$Posterior[PSE$Condition=="IPEF"]-PSE$Posterior[PSE$Condition=="IPEG"]
IPEG_IPEG2 <- PSE$Posterior[PSE$Condition=="IPEG"]-PSE$Posterior[PSE$Condition=="IPEG2"]

PSE_dif<- cbind.data.frame("IPE-IPEG"=IPE_IPEG,
                          "IPEF-IPEG"=IPEF_IPEG,
                          "IPE-IPEG2"=IPE_IPEG2,
                          "IPEF-IPEG2"=IPEF_IPEG2, 
                          "IPEG-IPEG2"=IPEG_IPEG2)
PSE_dif.df<-PSE_dif
PSE_dif<- PSE_dif %>% gather("IPE-IPEG","IPEF-IPEG","IPE-IPEG2","IPEF-IPEG2","IPEG-IPEG2", key= Condition, value= Posterior)
violin_dif<- violin_bayes(PSE_dif)[[1]]
violin_dif +
  labs(title="Contrast of Prosocial simulation effect across experiments",x="Contrast", y = "Beta coefficient") + 
  stat_boxplot(geom = "errorbar", width = 0.1, coef=0.7)

# Summaries
violin_bayes(PSE_dif, CI_range = c(0.055, 0.945))[[2]]
# pd
p_direction(PSE_dif.df)
# % in ROPE
rope(PSE_dif.df,ci=1, range = c(-0.1, 0.1))
```


# Grading effect of prosocial simulation effect 
```{r}
Bayes_gen<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~Match_condition+HT_sex_c+HT_age_c+(Match_condition|participant)+
                      (Match_condition|Sim_SID)+(Match_condition|HTFace_ID)+(Match_condition|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))

# Diagnostic Checks: pp check and traceplots
pp_check(Bayes_gen);plot(Bayes_gen)
# Rhat and sample sizes
bayes_samples(Bayes_gen)

# Summary
summary(Bayes_gen, prob=0.89)
# pd
p_direction(Bayes_gen, parameters = "b_Match_condition")
# % in ROPE
rope(Bayes_gen,ci=1, range = c(-0.10, 0.10), parameters ="b_Match_condition")

# BF01
BF01<- hypothesis(Bayes_gen, hypothesis =c("Match_conditionHTMHSM - Match_conditionHTPHSM=0",
                                           "Match_conditionHTMHSM - Match_conditionHTMHSP=0",
                                           "Match_conditionHTMHSM - Match_conditionHTPHSP=0",
                                           "Match_conditionHTPHSM - Match_conditionHTMHSP=0",
                                           "Match_conditionHTPHSM - Match_conditionHTPHSP=0",
                                           "Match_conditionHTMHSP - Match_conditionHTPHSP=0" ) , alpha=0.055)
BF01;plot(BF01)

# Extract posterior samples 
set.seed(67);posterior_gen<- posterior_samples(Bayes_gen) 
latent_SD(posterior_gen)
```

### Violn plots
```{r}
gen_effect<- cbind.data.frame("HT-HS-"= posterior_gen$b_Match_conditionHTMHSM,
                              "HT+HS-"= posterior_gen$b_Match_conditionHTPHSM,
                              "HT-HS+"= posterior_gen$b_Match_conditionHTMHSP,
                              "HT+HS+"= posterior_gen$b_Match_conditionHTPHSP)
gen_effect.df<-gen_effect
gen_effect<- gen_effect %>%gather("HT-HS-", "HT+HS-", "HT-HS+", "HT+HS+", key= Condition, value= Posterior)
violin_gen<- violin_bayes(gen_effect)[[1]]
violin_gen +
  labs(title="Grading effect of generalization",x="Condition", y = "Beta coefficient") +
  stat_boxplot(geom = "errorbar", width = 0.1, coef=0.7)
# Summary
violin_bayes(gen_effect, CI_range=c(0.055, 0.945))[[2]]
#-------------------------------------------------------------------------------------------------------------
# Plot the predicted probability of each category on the outcome measure for each condition
Gen_plot<-conditional_effects(Bayes_gen,categorical=T)
plot(Gen_plot)[[1]] +
  scale_x_discrete(labels=c("Identify Media Source", "HT-HS-", "HT+HS-", "HT-HS+", "HT+HS+")) +
  theme_classic() +
  xlab("Simulation Conditions") +
  ylim (0, 0.45)
#-------------------------------------------------------------------------------------------------------------
cond_contrasts<- BF01$samples
colnames(cond_contrasts) <- c("HT-HS->HT+HS-","HT-HS->HT-HS+","HT-HS->HT+HS+","HT+HS->HT-HS+","HT+HS->HT+HS+","HT-HS+>HT+HS+")
cond_contrasts.df <- cond_contrasts
cond_contrasts.df<-cond_contrasts.df %>% gather("HT-HS->HT+HS-","HT-HS->HT-HS+","HT-HS->HT+HS+","HT+HS->HT-HS+","HT+HS->HT+HS+","HT-HS+>HT+HS+",key= Condition, value= Posterior)
contrast_plot<- violin_bayes(cond_contrasts.df)[[1]]
contrast_plot+
  labs(title="Contrasts between conditions",x="contrasts", y = "Beta coefficient") +
  stat_boxplot(geom = "errorbar", width = 0.1, coef=0.7) + 
  geom_hline(yintercept=c(-0.1, 0.1),color="blue",linetype="dashed")

# Summary
violin_bayes(cond_contrasts.df, CI=c(0.055, 0.945))[[2]]
# pd
p_direction (cond_contrasts)
# % in ROPE
rope(cond_contrasts,ci=1, range =c(-0.10, 0.10))
```




### Order restricted model - include identify
* Models to be compared
** 1) a null model M0: all conditions (including control) are ~ equal
** 2) Unrestricted model Mu1: Identify != HT-HS- = HT+HS- = HT-HS+ = HT+HS+
** 3) Unrestricted model Mu2: Identify != HT-HS- != HT+HS- != HT-HS+ != HT+HS+
** 4) Unrestricted model Mu3: Identify != HT-HS- = HT+HS- = HT-HS+ != HT+HS+
** 5) ordered model1 M1:  Identify < HT-HS- = HT+HS- = HT-HS+ = HT+HS+
** 6) ordered model2 (theory driven) M2: Identify < HT-HS- < HT+HS- = HT-HS+ < HT+HS+
** 7) ordered model3 (data driven) M3: Identify < HT-HS- = HT+HS- = HT-HS+ < HT+HS+

```{r}
# Mu1
Bayes<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~Conditions+HT_sex_c+HT_age_c+(Conditions|participant)+
                      (Conditions|Sim_SID)+(Conditions|HTFace_ID)+(Conditions|STFace_ID)+(Conditions|HS_ID)) +
                   lf(disc~ 0+Conditions, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T, control=list(adapt_delta=0.99))
# Mu2
Bayes_gen<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~Match_condition+HT_sex_c+HT_age_c+(Match_condition|participant)+
                      (Match_condition|Sim_SID)+(Match_condition|HTFace_ID)+(Match_condition|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))
# Mu3
Bayes_mu3<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~ORM_code+HT_sex_c+HT_age_c+(ORM_code|participant)+
                      (ORM_code|Sim_SID)+(1|HTFace_ID)+(1|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+ORM_code, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup = 2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))

# Null model 
null<- brm(data= IPEG2.df, family=cumulative("logit"), 
                  Help~HT_sex_c+HT_age_c+(1|participant)+(1|Sim_SID)+(1|HTFace_ID)+(1|STFace_ID)+(1|HS_ID),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd)), 
                  iter=7000,warmup=2000,chains=8, cores=8, seed=67, sample_prior=T, save_all_pars = T ,control=list(adapt_delta=0.99))

levels(IPEG2.df$ORM_code)
# Mu3
Bayes_mu3<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~ORM_code+HT_sex_c+HT_age_c+(ORM_code|participant)+
                      (ORM_code|Sim_SID)+(1|HTFace_ID)+(1|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+ORM_code, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup = 2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))
set.seed(67);posterior_mu3<- posterior_samples(Bayes_mu3)
```
#### BFs
```{r}
 # Mu1/M0
set.seed (67);BF_Mu1_vs_M0 <- bayes_factor(Bayes, null)
(BF_M0_vs_Mu1 <- 1/BF_Mu1_vs_M0$bf)
# Mu2/M0
set.seed (67);BF_Mu2_vs_M0 <- bayes_factor(Bayes_gen, null)
(BF_M0_vs_Mu2 <- 1/BF_Mu2_vs_M0$bf)
# Mu3/M0
set.seed (67);BF_Mu3_vs_M0 <- bayes_factor(Bayes_mu3, null)
(BF_M0_vs_Mu3 <- 1/BF_Mu3_vs_M0$bf)

## Ordered Restricted model 1
m1<- (posterior[, "b_ConditionsImagine"]>0) 
(BF_M1_vs_Mu1<-restricted_BF(m1, 4e4, 2))

## Order restricted model 2
m2<-(posterior_gen[, "b_Match_conditionHTMHSM"]>0) & 
  (posterior_gen[, "b_Match_conditionHTMHSM"] < posterior_gen[, "b_Match_conditionHTPHSM"]) &
  (abs(posterior_gen[, "b_Match_conditionHTPHSM"] - posterior_gen[, "b_Match_conditionHTMHSP"]) < 0.1) &
  (posterior_gen[, "b_Match_conditionHTPHSP"] > posterior_gen[, "b_Match_conditionHTMHSP"])
(BF_M2_vs_Mu2<-restricted_BF(m2, 4e4, 5))

## Order restricted model 3
m3<-(posterior_mu3[, "b_ORM_codeImagine"] > 0) & 
    (posterior_mu3[, "b_ORM_codeImagine"] < posterior_mu3[, "b_ORM_codeHTPHSP"])
(BF_M3_vs_Mu3<-restricted_BF(m3, 4e4, 3))

# Bayes factors
BF_M0_vs_M1<- BF_M0_vs_Mu1 / BF_M1_vs_Mu1
BF_M0_vs_M2<- BF_M0_vs_Mu2 / BF_M2_vs_Mu2
BF_M0_vs_M3<- BF_M0_vs_Mu3 / BF_M3_vs_Mu3
BF_M1_vs_Mu2<- BF_M0_vs_Mu2 / BF_M0_vs_M1
BF_M3_vs_Mu2 <- BF_M0_vs_Mu2 / BF_M0_vs_M3
BF_M1_vs_M2 <- BF_M1_vs_Mu2 / BF_M2_vs_Mu2
BF_M2_vs_M3 <- BF_M2_vs_Mu2 / BF_M3_vs_Mu2
BF_M1_vs_M3 <- BF_M1_vs_M2 * BF_M2_vs_M3

# BFs
print(paste0("M0/M3: ", BF_M0_vs_M3))
print(paste0("M0/M1: ", BF_M0_vs_M1))
print(paste0("M0/M2: ", BF_M0_vs_M2))
print(paste0("M0/Mu2: ", BF_M0_vs_Mu2))

print(paste0("M3/M1: ", 1/BF_M1_vs_M3))
print(paste0("M3/M2: ", 1/BF_M2_vs_M3))
print(paste0("M3/Mu2: ", BF_M3_vs_Mu2))

print(paste0("M1/M2: ", BF_M1_vs_M2))
print(paste0("M1/Mu2: ", BF_M1_vs_Mu2))

print(paste0("M2/Mu2: ", BF_M2_vs_Mu2))
```


```{r}
Bayes<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~Conditions+HT_sex_c+HT_age_c+(Conditions|participant)+
                      (Conditions|Sim_SID)+(Conditions|HTFace_ID)+(Conditions|STFace_ID)+(Conditions|HS_ID)) +
                   lf(disc~ 0+Conditions, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T, control=list(adapt_delta=0.99))

Bayes_gen<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~Match_condition+HT_sex_c+HT_age_c+(Match_condition|participant)+
                      (Match_condition|Sim_SID)+(Match_condition|HTFace_ID)+(Match_condition|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))

# Null model 
null<- brm(data= IPEG2.df, family=cumulative("logit"), 
                  Help~HT_sex_c+HT_age_c+(1|participant)+(1|Sim_SID)+(1|HTFace_ID)+(1|STFace_ID)+(1|HS_ID),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd)), 
                  iter=7000,warmup=2000,chains=8, cores=8, seed=67, sample_prior=T, save_all_pars = T ,control=list(adapt_delta=0.99))

# Mu3
Bayes_mu3<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~ORM_code+HT_sex_c+HT_age_c+(ORM_code|participant)+
                      (ORM_code|Sim_SID)+(1|HTFace_ID)+(1|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+ORM_code, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup = 2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))


# Mu1/M0
set.seed (67);BF_Mu1_vs_M0 <- bayes_factor(Bayes, null)
# Mu2/M0
set.seed (67);BF_Mu2_vs_M0 <- bayes_factor(Bayes_gen, null)
# Mu3/M0
set.seed (67);BF_Mu3_vs_M0 <- bayes_factor(Bayes_mu3, null)
BF_Mu1_vs_M0;BF_Mu2_vs_M0;BF_Mu3_vs_M0

# Mu1/M0
set.seed (67);BF_Mu1_vs_M0.2 <- bayes_factor(Bayes.2, null.2)
# Mu2/M0
set.seed (67);BF_Mu2_vs_M0.2 <- bayes_factor(Bayes_gen.2, null.2)
# Mu3/M0
set.seed (67);BF_Mu3_vs_M0.2 <- bayes_factor(Bayes_mu3.2, null.2)
BF_Mu1_vs_M0.2;BF_Mu2_vs_M0.2; BF_Mu3_vs_M0.2






# Mu1
Bayes.2<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~Conditions+(Conditions|participant)+
                      (Conditions|Sim_SID)+(Conditions|HTFace_ID)+(Conditions|STFace_ID)+(Conditions|HS_ID)) +
                   lf(disc~ 0+Conditions, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T, control=list(adapt_delta=0.99))

# Mu2
Bayes_gen.2<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~Match_condition+(Match_condition|participant)+
                      (Match_condition|Sim_SID)+(Match_condition|HTFace_ID)+(Match_condition|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))

# Mu3
Bayes_mu3.2<- brm(data=IPEG2.df, family=cumulative("logit"),
                      formula= bf(Help~ORM_code+(ORM_code|participant)+
                      (ORM_code|Sim_SID)+(ORM_code|HTFace_ID)+(ORM_code|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+ORM_code, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))

# M0
null.2<- brm(data= IPEG2.df, family=cumulative("logit"), 
                  Help~ (1|participant)+(1|Sim_SID)+(1|HTFace_ID)+(1|STFace_ID)+(1|HS_ID),
                  prior= c(prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd)), 
                  iter=7000,warmup=2000,chains=8, cores=8, seed=67, sample_prior=T, save_all_pars = T,control=list(adapt_delta=0.99))



```



### Order restricted model- NC
* Models to be compared
** 1) a null model M0: all imagine helping conditions are ~ equal
** 2) Unrestricted model Mu1: HT-HS- != HT+HS- != HT-HS+ != HT+HS+
** 3) Unrestricted model Mu2: HT-HS- = HT+HS- = HT-HS+ != HT+HS+
** 5) ordered model1 (theory driven) M1: HT-HS- < HT+HS- = HT-HS+ < HT+HS+
** 6) ordered model2 (data driven) M2: HT-HS- = HT+HS- = HT-HS+ < HT+HS+

```{r}
no_control.df<-IPEG2.df[IPEG2.df$Match_condition!="Identify",]

# Null model 
null_NC<- brm(data= no_control.df, family=cumulative("logit"), 
                  Help~HT_sex_c+HT_age_c+(1|participant)+(1|Sim_SID)+(1|HTFace_ID)+(1|STFace_ID)+(1|HS_ID),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd)), 
                  iter=7000,warmup=2000,chains=8, cores=8, seed=67, sample_prior=T, save_all_pars = T ,control=list(adapt_delta=0.99))
# Mu1
Bayes_gen_NC<- brm(data=no_control.df, family=cumulative("logit"),
                      formula= bf(Help~Match_condition+HT_sex_c+HT_age_c+(Match_condition|participant)+
                      (Match_condition|Sim_SID)+(Match_condition|HTFace_ID)+(Match_condition|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+Match_condition, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup =2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))
set.seed(67);posterior_gen_NC<- posterior_samples(Bayes_gen_NC) 
# Mu2
Bayes_mu2_NC<- brm(data=no_control.df, family=cumulative("logit"),
                      formula= bf(Help~ORM_code+HT_sex_c+HT_age_c+(ORM_code|participant)+
                      (ORM_code|Sim_SID)+(1|HTFace_ID)+(1|STFace_ID)+(1|HS_ID)) +
                   lf(disc~ 0+ORM_code, cmc=F),
                  prior= c(prior(normal (0,1), class=b),
                           prior(normal(0,1.2), class=Intercept),
                           prior(exponential(1), class= sd),
                           prior(lkj(1), class = cor)),
                  iter=7000,warmup = 2000, chains=8, cores=8, seed=20, sample_prior=T,save_all_pars = T,control=list(adapt_delta=0.99))
set.seed(67);posterior_mu2_NC<- posterior_samples(Bayes_mu2_NC)



```
#### BFs
```{r}
# Mu1/M0
set.seed (67);BF_Mu1_vs_M0_NC <- bayes_factor(Bayes_gen_NC, null_NC)
BF_M0_vs_Mu1_NC <- 1/BF_Mu1_vs_M0_NC$bf
# Mu2/M0
set.seed (67);BF_Mu2_vs_M0_NC <- bayes_factor(Bayes_mu2_NC, null_NC)
BF_M0_vs_Mu2_NC <- 1/BF_Mu2_vs_M0_NC$bf

# Order restricted model 1
m1_NC<- (posterior_gen_NC[, "b_Match_conditionHTPHSM"]>0) &
  (abs(posterior_gen_NC[, "b_Match_conditionHTPHSM"]-posterior_gen_NC[, "b_Match_conditionHTMHSP"])<0.1) &
  (posterior_gen_NC[, "b_Match_conditionHTPHSP"]>posterior_gen_NC[, "b_Match_conditionHTMHSP"])
(BF_M1_vs_Mu1<-restricted_BF(m1_NC, 4e4, 4))

# Order restricted model 2
m2_NC<-(posterior_mu2_NC[, "b_ORM_codeImagine"] < 0) 
(BF_M2_vs_Mu2<-restricted_BF(m2_NC, 4e4, 2))


# Bayes factors
BF_M0_vs_M1_NC <-  BF_M0_vs_Mu1_NC / BF_M1_vs_Mu1
BF_M0_vs_M2_NC <- BF_M0_vs_Mu2_NC / BF_M2_vs_Mu2
BF_Mu2_vs_M1_NC <- (1/ BF_M0_vs_Mu2_NC) * BF_M0_vs_M1_NC
BF_M2_vs_M1_NC <- BF_M0_vs_M1_NC / BF_M0_vs_M2_NC

# BFs
print(paste0("M0/M2: ", BF_M0_vs_M2_NC))
print(paste0("M0/Mu: ", BF_M0_vs_Mu2_NC))
print(paste0("M0/M1: ", BF_M0_vs_M1_NC))

print(paste0("M2/Mu: ", BF_M2_vs_Mu2))
print(paste0("M2/M1: ", BF_M2_vs_M1_NC))

print(paste0("Mu/M1: ", BF_Mu2_vs_M1_NC))

```



























